---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  out.width = "100%"
)
```

# errormindR: Efficient Error Debugging and Handling with AI

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

Disclaimer: This package is a prove of concept and contains only two functions. It's not recommended for production.

The goal of `errormindR` is to provide a friendly interface to communicate with an AI/LLM to explain an error and provide a solution right in the RStudio editor.

Future plan: the ultimate goal of the package is to automatically replace the failing parts of a program. Think of this that you've some programs that run based on schedule, but something unexpected causes failure. This tool can be called (future versions) as an extra layer of safety to debug the code, test the output against the previous version and keep a log of these changes.

This package uses `ellmer` package behind the scene to communicate with an LLM. The default model is "gpt-4.1" from OpenAI, but you can provide your own.
Additionally, you may need to set up your API key if this is your first time using LLM via API. Here's a brief [guide](https://ellmer.tidyverse.org/reference/chat_openai.html?q=OPENAI_API_KEY#arg-api-key) how set it up in your RStudio.

Lastly, this package uses `rstudioapi` package here and there, and entirely tested in RStudio. If you're using it in a different IDE, it may not work as expected.

## Installation

You can install the development version of `errormindR` from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("thesherzad/errormindR")
```

## Example

This is a basic example which shows how you can call it:

```{r eval=FALSE}
library(errormindR)
log("123") |> minerr()

# or
df <- data.frame(x = c("Jan", "Feb", "Mar", "Apr", "May", "June", "Jul"))
df |> dplyr::filter(x == "Jun") |>
  minerr(is_logical_error = TRUE,
         chat = "expecting to get some record, but getting nothing")

# after that's run
minerr_log()
```

Note: This package uses `tempdir()` to store the logs temporarily within user's session.
